### 2020-05-28 writeup/transfer.tex
changes

\subsection{Contributing causes of negative transfer}

@@

\textbf{Implications.}
We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.

\begin{proposition}\label{prop_var_transition}
	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
	We derive the following transition as a parameter of $\sigma_1^2$:
	\begin{itemize}
		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\sigma_1^2 > - \frac12p d^2 \cdot \rho_1 +\left(1+ \frac32\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}
As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
The details can be found in Appendix \ref{app_proof_31}.

@@

\begin{proposition}\label{prop_var_transition}
	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 40$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
	We derive the following transition as a parameter of $\sigma_1^2$:
	\begin{itemize}
		\item If $\sigma_1^2 \le p d^2 \cdot \rho_1 +\left(1+ \frac12 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\sigma_1^2 > p d^2 \cdot \rho_1 +\left(1+ 2\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}
As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
The details can be found in Appendix \ref{app_proof_31}.

>>>>

\subsection{Contributing causes of negative transfer}\label{sec_similarity}

@@

@@

\begin{proposition}\label{prop_var_transition}
	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
	We derive the following transition as a parameter of $\sigma_1^2$:
	\begin{itemize}
		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\sigma_1^2 > - \frac12\rho_1\cdot p d^2   +\left(1+ \frac32\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}
As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
The details can be found in Appendix \ref{app_proof_31}.
